Stable Neo-Hookean Flesh Simulation

### 2019-11-25 LaTeX-Master-Vorlage/chapter/Background.tex
working on background and paper

@@

\section{Deformation}
When applying a force over an object naturally the object itself undergoes a deformation. In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.

>>>>

\todoredefined[inline]{
TODO: positive definite matrices definition and lemmas, orthogonal, etc.
}

@@

\section{Deformation}
When applying a force over an object naturally the object itself undergoes a deformation. In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area:

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on background and paper

\section{Energy Formulation}
The core goal of the paper was to model deformations for virtual characters that have human-like features. They concentrated on the deformation energy. In order to achieve a convincing result as a first step we need to specify some requirements. For our needs in this case the stability of the energy is important. More precisely we need a hyperelastic energy that is stable in the following four important ways:

@@

>>>>

\section{Deformation Gradient}

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathrm{F=RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathrm{F})$ & Relative volume change \\ \hline
    $\mathrm{C}=\mathrm{F}^{T} \mathrm{F}$ & Right Cauchy-Green  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathrm{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption{Quantities Derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:1}
\end{table}

\todoredefined[inline]{
TODO: Add in Background? Explain more each entity
}

\section{Energy Formulation}

\subsection{Stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. They concentrated on the deformation energy. In order to achieve a convincing result as a first step we need to specify some requirements. For our needs in this case the stability of the energy is important. More precisely we need a hyperelastic energy that is stable in the following four important ways:

@@

\subsection{Existing Neo-Hookean Energies}
A commonly used energy function is defined as follows (see e.g. \cite{bonet1997nonlinear}, p.148):

\[
\Psi=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}
\]

where $\lambda$ and $\mu$ are the material constants and $J = det(F)$.

In the literature appear many more different formulations of the energy. Each one consists of a 1D length term and a 3D volume term.

\textbf{1D Length Term:} This term penalizes length changes.

\textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term.

\subsection{Rest Stabilization}

\subsection{Lamé Reparametrization}
